Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
poor @metaphori bring him back into the group

\author{
\IEEEauthorblockN{
    Nicolas Farabegoli\IEEEauthorrefmark{1},
    Danilo Pianini\IEEEauthorrefmark{1},
    Roberto Casadei\IEEEauthorrefmark{2},
    Mirko Viroli\IEEEauthorrefmark{1}
}
\IEEEauthorblockA{\textit{Department of Computer Science and Engineering} \\
\textit{Alma Mater Studiorum---Università di Bologna}\\
Cesena, Italy \\
\IEEEauthorrefmark{1}\{nicolas.farabegoli,danilo.pianini,mirko.viroli\}@unibo.it}
\IEEEauthorrefmark{2}roby.casadei@unibo.it
}

>>>>

\author{
\IEEEauthorblockN{
    Nicolas Farabegoli,
    Danilo Pianini,
    Roberto Casadei,
    Mirko Viroli
}
\IEEEauthorblockA{\textit{Department of Computer Science and Engineering} \\
\textit{Alma Mater Studiorum---Università di Bologna}\\
Cesena, Italy \\
\{nicolas.farabegoli, danilo.pianini, roby.casadei, mirko.viroli\}@unibo.it}
}
